%!TEX root = ClementiCooperBarba2018.tex

Extending \pygbe to the LSPR biosensing application required considerable code 
modifications and added functionality. The results presented in the previous section 
offer evidence to build confidence on the suitability of the mathematical model 
and the correctness of the code.
The grid-convergence study with a nanosphere under a constant electric field 
shows a $1/N$ rate of convergence, consistent with convergence results 
in previous work using \pygbe \cite{CooperBardhanBarba2013}.
Further verification of \pygbe's new ability to compute extinction cross-section
of a scatterer in the long-wavelength limit is provided in Figure \ref{fig:verif_sphere}.
The computed extinction cross-section of a silver nanoparticle in a range of frequencies 
is within 1\% of the analytical value, with the numerical parameters chosen.
This level of accuracy is likely sufficient, given that experimental uncertainty in 
the values of the dielectric constant for silver is in the order of 1\%, also \cite{JohnsonChristy1972}.

%\subsection{LSPR response to BSA}

Figure \ref{fig:2pz_response} shows a red shift of the plasmon resonance frequency peak in presence of the BSA proteins.
Experimental observations of Tang, et al.~\cite{TangETal2010} with silver nanoparticles of approximately 17 nm in diameter and BSA proteins in solution revealed a red shift upon adding the proteins. 
Similar to the effect we see with our model, they observed as well a decrement of 
the peak amplitude.
Moreover, recent experiments \cite{PuETal2018} report a resonance frequency for a silver nanoparticle in the presence of BSA proteins of between 380 and 400 nm, which is consistent with our results.
Other experiments \cite{RaphaelETal2013} also report a red shift in the resonance frequency in the presence of (different) proteins.
Our boundary element method approach using electrostatic
approximation is thus able to capture the characteristic resonance-frequency 
shift of LSPR biosensors.

With the electric field aligned in the $z$-direction, placing the proteins at a distance
in the $x$ or $y$ directions from the nanoparticle shows a negligible shift in the 
resonance peak: the shifts in Figure \ref{fig:2pxy_response} 
are smaller than the resolution between wavelengths ($< 0.25$ nm).
This finding is consistent with the free electrons oscillating in the $z$ direction
under a $z$-polarized electric field, and not in the $x$ and $y$ directions
(see Figure \ref{fig:lspr}). 
The analytes have a marked effect when placed in the $z$ direction, where
they can interfere with the free oscillating electrons. 

Figure \ref{fig:dist_response} shows how the  shift in resonance frequency varies 
with the distance between the sensor and the analyte. As expected, the shift decays 
as the BSA moves away from the sensor, to the point that if the BSA proteins are placed
$d=2$ nm away, the shift is only $0.25$ nm. This result shows the potential of \pygbe 
and the electrostatic approach to study biosensor sensitivity with distance.
Note that possible quantum effects (e.g., tunneling) at $d=0.5$nm are ignored with our classical model.
Even if this distance could be close to or in the quantum regime, evidence that classical theory is valid at this distance in similar systems has been reported 
\cite{SavageETal2012, EstebanETal2012}.  

Even though there is evidence that techniques such as Plasmon Enhanced Raman Scattering are capable of detecting all the way to single molecules \cite{ZhangZhangETal2013}, 
as far as we know, there is no evidence of purely LSPR approaches that can sense such low concentration of analytes.
These computational studies can shine light on  potential improvements that would enhance sensitivity of LSPR biosensors, for example, by using smaller ligands. 

We are not aware of other LSPR simulations where the molecular details of the analyte are considered, however, similar calculations could be performed with other software. 
For example, BEM++ \cite{SmigajETal2015} also models the system as a set of boundary integral equations, discretized in flat triangular panels. 
This software uses the Galerkin approach and algorithmic acceleration via hierarchical matrices, which is slower and less memory efficient than the treecode and limits the accessible problem sizes.
The Matlab toolbox MNPBEM \cite{HohenesterTrugler2012} is another alternative software designed to simulate scattering of metallic nanoparticles.
Its BEM implementation is similar to \pygbe as it uses a centroid collocation scheme on flat triangular panels, but differs in the algorithmic acceleration technique, which is also based on hierarchical matrices rather than a treecode. 
This results in higher memory usage compared to our code, making it harder to simulate large analytes in detail.
Commercial finite-element or finite-difference solvers could also be used in this application, for example, COMSOL. 
These volumetric approaches, however, struggle to correctly impose the zero boundary condition at infinity, which is exactly met for a BEM formulation.
